\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-22 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\date{September 2021}
 \maketitle
\bigskip

We would like to thank you for your insightful comments. They led us to introduce some
significant changes to the paper that we hope address your concerns. We first give you an overview
of the revision (Section\ref{sec:main_changes}) before answering in detail each of your comments (Section\ref{sec:detailed_answers}). Number of sections, pages and equations mentioned in the text refer to the revised version. When necessary, we refer to number of sections, pages and equations from the submitted version. In this case, they are written between brackets.

\section{Main changes \label{sec:main_changes}}

The structure of the paper has been modified after taking into account the referees' comments.
\begin{itemize}
\item In the submitted version, [Section 2] was devoted to the estimation of international transport costs; specifically, their break-down in two components, additive and ad-valorem. In [Section 3], we investigated the role of additive costs in the decomposition of transport costs time trends, between structural changes and composition effects. [Section 4] was devoted to the robustness analysis relative to the results from both previous sections.
\item In the revised version, we have strengthened the robustness checks regarding the estimation results of international transport costs (robustness checks to aggregation and to endogeneity have been added). Accordingly, the previously-called [Section 2] has been split in two Sections: Section 2, where we present the data and the estimation strategy; and Section 3, which presents the results and now includes the robustness checks as a final sub-section. For sake of brevity, the robustness analysis related to composition effects has been sent to the Appendix (Section C.3).
\item Both referees asked us to highlight the implications of additive costs (the ``Big Picture''). We agree that this was not enough emphasized in the submitted version, and we thank the referees for their suggestions on that issue. The revised version answers this concern in two points.
    \begin{enumerate}
    \item We maintain the analysis of the transport costs time trends (previously [Section 3], now Section 4); but we improved this section’s readibility by leaving the technical aspects in the Appendix (Section C). As such, we hope that the main message of this Section is easier to understand.
    \item Most importantly, we now emphasize the ``Big Picture'' welfare implications of additive costs on theoretical grounds. Through the lens of the \cites{melitz} model amended to integrate additive costs, we analyze the welfare gains that derive from the reduction in international transport costs that we have estimated in Section 3, to quantify the extra welfare gains attributable to the reduction of their additive component. This analysis is conducted in a new Section 5.
        \end{enumerate}
\item To keep the paper (both the main text and with appendix included) within a reasonable number of pages, yet to be fully transparent about our results, we have added numerous detailed tables to the Online Appendix.
\end{itemize}

@@

We now answer in detail each of your comments given in italics.

\section{Detailed answers \label{sec:detailed_answers}}

\subsection{Critique 1: Empirical Strategy}

\textit{Using the notation of the authors, they are interested
in identifying the share of the specific cost in the total transport cost. Namely,}
\begin{eqnarray*}
&& \frac{\frac{t_{is(k)}}{\tilde{p}_{ik}}}{\tau_{is(k)}-1 + \frac{t_{is(k)}}{\tilde{p}_{is(k)}}} \\
\text{or,} &&\frac{t_{is(k)}}{(\tau_{is(k)}-1)\tilde{p}_{is(k)} + t_{is(k)}}
\end{eqnarray*}

@@

These three points indeed deserve careful consideration. We provide separate answers to each of them below.

%\subsubsection{On the justifications for our empirical approach}

\subsubsection{Concern (i): About the assumption of separability}
Our main empirical equation and its underlying assumptions regarding the separability of transport costs between their country- and product-level components draw on the one proposed by \citet{Irrazabal_2015} to estimate the share of additive costs in a firm-level context. It relies on a simple theoretical framework with minimal assumptions, and is compatible with most approaches within the so-called category of ``New Trade Theories''.

Further, we provide a robustness check for this separability assumption that $\tau_{ik} = \tau_i\tau_{k}$ and
 $t_{ik} = t_i +t_k$ in Section 3.3.1 of the paper (Table 2) \textbf{XXX CHECK AT THE END XXX}). We check the robustness of our results by re-running the estimation without the separability assumption. This comes at the cost of a substantial increase in the number of fixed in the regression. In 2019, for example, there are 14,016 country*sector pairs. Adding 28,032 fixed effects (number of country pairs $\times2$ for the two additive and multiplicative costs fixe effects) rather than ``only'' 836 ($(188+230)\times 2$). This is computationally not tractable.
% use "/Users/guillaumedaudin/Documents/Recherche/2013 -- Trade Costs -- local/data/hummels_tra.dta", clear
% keep if year==2019
% keep if mode=="ves"
% gen sector=substr(sitc2,1,3)
% gen blouk = iso_o+sector
% codebook blouk
 For this reason, we have decided to run the robustness check on a reduced sample.
 We select, for each year, the largest importers that form together at least 80\% of annual trade and the largest traded sectors that form together at least 80\% of annual trade.
 We keep in the sample all trade observations from these importers and in these sectors.
 This sample is smaller in terms of observations (2,125 for Air, 5,260 for Vessel on average over the period 1974-2019 (see Table 2), vs more than 30,000 on the complete sample, see Table 1), yet it remains quite large in terms of trade coverage.\footnote{In the restricted sample, we have around 25 sectors from 14 countries for Air transport, vs 230 sectors from 190 countries in the large sample; and around 50 sectors from 20 countries for Vessel, vs 600 sectors from 190 countries in the complete sample). The vast majority of US imports comes from a selected range of countries, in a selected range of sectors. \textbf{LP: CHECK THE NUMBERS}}.
 As we conclude at the end of Section 3.3.1, whatever the transport mode and for both types of transport costs, the trend patterns of international transport costs are very similar whether estimated under the separability assumption or not.
 %- see in particular Figures 6 and 7 on pp. 25-26 \textbf{XXX CHECK AT THE END XXX}. Given that the restricted sample covers 80\% of the total trade flows of the US economy, we hope to convince you that this result can be extended to the whole dataset.

@@

\begin{equation}
\ln\left(\frac{p_{ik}}{p^u_{ik}}-1 \right)= \ln \left(\tau_{is(k)} -1+\frac{t_{is(k)} }{p^u_{ik}} \right) + \epsilon_{ik} \label{eq:model_IetA}
\end{equation}
\noindent where $p^u_{ik}$ refers to the unit price associated with quantity. Depending on the sector, two different units are considered, kilograms and numbers.

The results are the following ... \textbf{To DEVELOP}

\end{enumerate}

These motives altogether highlight that it would be too costly in our context to switch from weights to quantities to compute unit prices for our baseline regression. We hope to convince you that \textbf{XXX TO BE COMPLETED XXX}

### 2021-10-22 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Travail sur séparabilité answer referee1 et papie
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\subsubsection{Robustness to the separability assumption}
In this section, we provide a robustness analysis to the separability assumption of country-good fixed effects, which considers (following \citealp{Irrazabal_2015}) that both the ad-valorem and the additive costs are separable between the origin country ($i$) and the product ($s(k)$) dimensions.
That is, we relax Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to model $\tau_{is(k)}$ and $t_{is(k)}$ (on a yearly/transport mode basis).
Yet, this comes at the cost of having to estimate a much larger number of fixed effects (for approx. 200 countries of origin and 200 sectors at the 3-digit level, this means estimating 40,000 versus 400 fixed effects, per year and per transport mode), making the estimation (all the more given our non-linear setting) intractable in practice.
This drives us to conduct the analysis on a sub-sample of trade flows, upon which two estimations are conducted (for every year and each transport mode): with the separability assumption (Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) hold, our baseline case) and without.
For each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows. Table \ref{tab:robustness_separability} shows a summary of the results, considering the average estimated values over the period (by transport mode). \textbf{LP: Pb avec le nb d'observations. }
%
%\begin{table}[htbp]
%  \centering
%  \caption{Robustness to the separability assumption (average over the period) - restricted sample}
%\begin{center}
%    \begin{tabular}{lcc|cc}
%    \hline \hline
%    \multicolumn{5}{c}{Mean value over 1974-2019} \\
% \multicolumn{5}{c}{3 digits} \\    \hline \hline
%   Mode  & \multicolumn{2}{c|}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
%   Separability & No  & Yes (baseline) & No & Yes (baseline)\\ \hline
%    \multicolumn{5}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$.
%in \%)}  \\
%    Mean  & 1.76 & 1.96 & 2.61 & 2.99 \\
%    Median &0.65 & 0.84 &1.83 & 2.23 \\ \hline
%    \multicolumn{5}{l}{\textit{Ad-valorem term} ($\widehat{\tau}$, in \%)}\\
%    Mean  & 1.04 & 0.94 & 2.43 & 2.40 \\
%    Median & 0.56 & 0.83 & 2.06 & 2.04 \\ \hline
%\multicolumn{5}{l}{\textit{Share of additive costs in total costs (in \%)}} \\
%    Mean  & 62.8  & 67.5  & 51.8  & 55.4 \\
%    Median & 54.1  & 50.5  & 47.0  & 52.2 \\  \hline
% \textit{Diagnostic test} & & &  &  \\
%    %$R^2$    & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.68} & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.45} \\
%    %SER   & \multicolumn{1}{c}{0.57} & \multicolumn{1}{c}{0.72} & \multicolumn{1}{c}{0.53} & \multicolumn{1}{c}{0.69} \\
%    AIC criteria & 4657.60 & 4654.23 & 10744.83 & 10690.80 \\ \hline
%    %Log-likelihood & \multicolumn{1}{c}{-1757.75} & \multicolumn{1}{c}{-2258.24} & \multicolumn{1}{c}{-4018.51} & \multicolumn{1}{c}{-5220.00} \\ \hline
%\# observations & 2381 & 2381 & 2798 & 2798 \\
%\# origin country & 13.4 & 13.4 & 19.8 & 19.8 \\
%\# products & 25.5 & 25.5 & 53 & 53 \\ \hline \hline
%    \end{tabular}%
%\end{center}
%\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule: for each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows.
%The additive term is expressed in fraction of fas price. 1989 omitted in 3-digit estimation for air.}}
%\label{tab:robustness_separability}
%\end{table}

\begin{table}[htbp]
	\centering
	\caption{Robustness to the separability assumption - restricted sample}
	\begin{center}
			\input{Table4_reshaped.tex}
	\end{center}
	\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule: for each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows.
			The additive term is expressed in fraction of fas price.}}
	\label{tab:robustness_separability}
\end{table}

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but 80\% of the total value of aggregated trade) involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the results on a detailed yearly basis and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triple $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, \textbf{Section XXX} for sake of space saving.} %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians

>>>>

\subsubsection{Robustness to the separability assumption}
In this section, we provide a robustness analysis to the separability assumption of country-good fixed effects, which considers (following \citealp{Irrazabal_2015}) that both the ad-valorem and the additive costs are separable between the origin country ($i$) and the product ($s(k)$) dimensions.
That is, we relax Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) to model $\tau_{is(k)}$ and $t_{is(k)}$ (on a yearly/transport mode basis).
Yet, this comes at the cost of having to estimate a much larger number of fixed effects (for approx. 200 countries of origin and 200 sectors at the 3-digit level, this means estimating 40,000 versus 400 fixed effects, per year and per transport mode), making the estimation (all the more given our non-linear setting) intractable in practice.
This drives us to conduct the analysis on a sub-sample of trade flows, upon which two estimations are conducted (for every year and each transport mode): with the separability assumption (Equations (\ref{eq:ad-valorem}) and (\ref{eq:add}) hold, our baseline case) and without.
For each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows. Table \ref{tab:robustness_separability} shows a summary of the results, considering the average estimated values over the period (by transport mode).
%\textbf{LP: Pb avec le nb d'observations. } GD : CELA A L’AIR BON ET ON LAISSE COMME CELA
%
%\begin{table}[htbp]
%  \centering
%  \caption{Robustness to the separability assumption (average over the period) - restricted sample}
%\begin{center}
%    \begin{tabular}{lcc|cc}
%    \hline \hline
%    \multicolumn{5}{c}{Mean value over 1974-2019} \\
% \multicolumn{5}{c}{3 digits} \\    \hline \hline
%   Mode  & \multicolumn{2}{c|}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
%   Separability & No  & Yes (baseline) & No & Yes (baseline)\\ \hline
%    \multicolumn{5}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$.
%in \%)}  \\
%    Mean  & 1.76 & 1.96 & 2.61 & 2.99 \\
%    Median &0.65 & 0.84 &1.83 & 2.23 \\ \hline
%    \multicolumn{5}{l}{\textit{Ad-valorem term} ($\widehat{\tau}$, in \%)}\\
%    Mean  & 1.04 & 0.94 & 2.43 & 2.40 \\
%    Median & 0.56 & 0.83 & 2.06 & 2.04 \\ \hline
%\multicolumn{5}{l}{\textit{Share of additive costs in total costs (in \%)}} \\
%    Mean  & 62.8  & 67.5  & 51.8  & 55.4 \\
%    Median & 54.1  & 50.5  & 47.0  & 52.2 \\  \hline
% \textit{Diagnostic test} & & &  &  \\
%    %$R^2$    & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.68} & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.45} \\
%    %SER   & \multicolumn{1}{c}{0.57} & \multicolumn{1}{c}{0.72} & \multicolumn{1}{c}{0.53} & \multicolumn{1}{c}{0.69} \\
%    AIC criteria & 4657.60 & 4654.23 & 10744.83 & 10690.80 \\ \hline
%    %Log-likelihood & \multicolumn{1}{c}{-1757.75} & \multicolumn{1}{c}{-2258.24} & \multicolumn{1}{c}{-4018.51} & \multicolumn{1}{c}{-5220.00} \\ \hline
%\# observations & 2381 & 2381 & 2798 & 2798 \\
%\# origin country & 13.4 & 13.4 & 19.8 & 19.8 \\
%\# products & 25.5 & 25.5 & 53 & 53 \\ \hline \hline
%    \end{tabular}%
%\end{center}
%\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule: for each year and transport mode, we select the countries ($i$) and the products (at the 3-digit level, $s(k)$) that constitute 80\% of the total value of trade flows.
%The additive term is expressed in fraction of fas price. 1989 omitted in 3-digit estimation for air.}}
%\label{tab:robustness_separability}
%\end{table}

\begin{table}[htbp]
	\centering
	\caption{Robustness to the separability assumption - restricted sample}
	\begin{center}
			\input{Table4_reshaped.tex}
			\input{Table4.tex}
	\end{center}
	\parbox[l]{12cm}{\footnotesize{Notes: Estimations are performed on a restricted sample, based on the following rule:  we select, for each year, the largest importers that form together at least 80\% of annual trade and the largest traded sectors that form together at least 80\% of annual trade. We keep in the sample all trade observations from these importers and in these sectors.
			The additive term is expressed in fraction of fas price.}}
	\label{tab:robustness_separability}
\end{table}

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but the vast majority of the total value of aggregated trade)
\textbf{Ce n’est pas 80\% du commerce : voir le mode de calcul. Je sais que vous allez me demander combien c’est et je n’ai pas de réponse toute faite. Je peux passer une heure ou deux à le calculer si vous voulez -- GD}] involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the results on a detailed yearly basis and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triple $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, \textbf{Section XXX} for sake of space saving.} %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians
